Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-21 WSSSPE3/report/wg_main_funding_spec_expert.tex
small edits

To find more information about this group, or join it, see \url{http://www.rse.ac.uk/groups}.

>>>>

A list of known UK research software engineering groups is available at  
\url{http://www.rse.ac.uk/groups}, and a list for the rest of the world
is at \url{http://www.rse.ac.uk/international}.
To add another group to the list, please make a pull request as requested
on either of these pages.
